---
title: "Querying TCGA data using BigQuery"
author: "Sean Davis"
date: "May 5, 2016"
output: html_document
---

```{r init}
library(bigrquery)
```


```{r listtables, eval=FALSE}
bigrquery::list_tables("isb-cgc", "tcga_201510_alpha")
```

The first time you run this, you will be likely asked to login to a google billing account. This process will
involve R kicking you over to a web browser (the first time) where you will need to login to your
google cloud project. You will likely see this type of message....

```
Use a local file to cache OAuth access credentials between R sessions?
1: Yes
2: No

Selection: Yes
Adding ^\.httr-oauth$ to .Rbuildignore
Waiting for authentication in browser...
Press Esc/Ctrl + C to abort
Authentication complete.
```

Assuming that you have set up an account with the ISB Cancer Genomics 
Cloud Pilot, you can authorize R to access the account, and from then on will be able to operate without
browser interaction.  

```{r listtables2}
bigrquery::list_tables("isb-cgc", "tcga_201510_alpha")
```

```{r sessionInfo}
sessionInfo()
```
