---
title: "NCI-IRP Cancer Genomics Cloud Workshop - Using R for Seven Bridges CGC"
author: "Steve Tsang"
# change date below
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
vignette: >
  %\VignetteIndexEntry{NCI-IRP Cancer Genomics Cloud Workshop - Using R for Seven Bridges CGC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8} 
---

This is the second workshop for the NCI Cancer Genomic Cloud Pilots. This document includes instructions to do the following tasks using the Seven Bridges API with the R client.  

This is a work-in-progress.

[Material for this workshop](http://teamcgc.nci.nih.gov.s3-website-us-east-1.amazonaws.com/)  
[Additional information can be found here - (Follow API V2)](https://github.com/sbg/sevenbridges-r)  

Pre-requisite  
R studio
<https://www.rstudio.com/products/rstudio/download/>  
Seven Bridges CGC account
<https://cgc.sbgenomics.com/login/>  
Login and retrieve your authorization token  

## Installation
Make sure you have the latest verion of bioconductor installed. (Updated 5/3/2016)

```{r}
#source("http://bioconductor.org/biocLite.R")
#useDevel(devel = TRUE)
#biocLite("sevenbridges")
```

For now, use github



## Authorization

````{r, eval=FALSE}
library(sevenbridges) 
a<-Auth(user="tsang", platform = "cgc", token = "XXX")

````

##  Navigate the CGC

````{r}
p<- a$project(id="tsang/hackathon")
##a$project()
##p$file()
p$file()[[1]]
p$file()[[1]]$download_url()

````

## Download Files
````{r, eval=FALSE}
fid = p$file()[[1]]$id
a$project("hackathon")[[2]]$file(id = fid)$download("~/Downloads/")

fls <-a$project("hackathon")$file()
download(fls, "~/Downloads/")
````

## Upload files
from my computer
````{r, eval=FALSE}
fl = "~/Downloads/count000.csv"
> p$upload(fl, overwrite=FALSE)

dir <- "~/Downloads/temp/"
list.files(dir)
p$upload(dir, overwrite=TRUE)

````

## Start a task with apps

````{r, eval=FALSE}
p<-a$project(id="tsang/temp-1")
p$app()
ap <- p$app()[[1]]
#RNAseq STAR DEseq2

a$project("temp-1")$app_add(name= "Draft rnaseq",
                            description = "test",
                            app = tsang/temp-1/rna-seq-STAR-deseq2,
                            inputs = list(min=1, max=10))
````

More to come...  






